% Section and frames
\section{CONCLUSIONS}
\label{conclusion}

% Section title slide
\sectiontitleframe{CONCLUSIONS}

% Slide 1
\begin{frame}{Concluding Remarks and Future Work}
    \frametitle{Concluding Remarks and Future Work}
    \begin{itemize}
        \item The project demonstrated the effectiveness of polynomial regression and regularized models in predicting house prices.
        \item Polynomial features prevented from overfitting and improved model accuracy.
        \item Future work could explore more advanced machine learning techniques like ensemble methods or neural networks for better performance.
        \item Incorporating additional trend data, like housing market trends or demographic trends, could further refine predictions.
    \end{itemize}
\end{frame}

% Slide 2
\begin{frame}{Application of Regression Models in Software Testing}
    \frametitle{Application of Regression Models in Software Testing}
    \begin{itemize}
        \item Regression models in ML-driven software testing aid in smart test case generation and predictive test planning.
        \item They enable automated, data-driven decision-making, improving testing efficiency and coverage.
        \item The integration of ML models can help in identifying critical testing areas, reducing manual workload and improving test accuracy.
    \end{itemize}
    \vspace{1cm}
    \center
    \tiny
    \textit{Source: "A Complete Guide To AI/ML Software Testing" \cite{katalon_ai_ml_testing}}
\end{frame}

% Slide 3
\begin{frame}{Regression Models in Testing in Production}
    \frametitle{Regression Models in Testing in Production}
    \begin{itemize}
        \item ML regression models enhance production testing by predicting system behavior and potential failures.
        \item These models are critical for analyzing and interpreting large volumes of production data in real-time.
        \item The insights gained aid in proactive decision-making and troubleshooting, thus improving system performance and reliability.    \end{itemize}
    \vspace{0.5cm}
    \center
    \tiny
    \textit{Source: "Using AI/ML and Production Data to Improve Software Testing". \cite{saucelabs_ai_ml_testing}}
\end{frame}




% Example frame 1
% \begin{frame}{frame} % set section name
%     \frametitle{frame}
%     \begin{itemize}
%         % Conclusion and Future Work
%         \item 1 slide
%         \item Concluding remarks/insights
%         \item How could this work be extended/improved in the future?
%         
%         % Possible Application in the Testing Domain
%         \item 1-2 slides
%         \item Describe some ideas how could selected ML/DL method/s be applied in the testing domain (area, type, problem, constraints…)
%         
%     \end{itemize}
% \end{frame}