% Section and Frames
\section{Conclusion and Next Steps}
\label{conclusion_section}

% Section title frame
\sectiontitleframe{Conclusion and Next Steps}

\begin{frame}{Potential Improvements and Future Plans}
    \frametitle{Potential Improvements and Future Plans}
    \begin{itemize}
        \item \textbf{Areas for Improvement:} Exploring automated selection of preprocessing steps and optimizing processing efficiency.
        \item \textbf{Framework Generalization:} Extending the framework's application beyond PCB defect detection to other image-based ML tasks.
        \item \textbf{Next Project Phase:} Development of the PCB Defect Detector Model, integrating the enhanced image preprocessing framework.
    \end{itemize}
    These future directions aim to refine and expand the framework, enhancing its utility and effectiveness in a broader range of applications.
\end{frame}

\begin{frame}{Conclusion}
    \frametitle{Conclusion and Invitation for Questions}
    \begin{itemize}
        \item \textbf{Key Takeaways:} The Image Preprocessing Framework is a versatile, efficient tool essential in PCB defect detection and potentially applicable in diverse ML contexts.
        \item \textbf{Framework's Role:} An integral part of the broader PCB defect detection project, enhancing the accuracy and reliability of defect identification.
        \item \textbf{Engagement:} Open to questions, feedback, and discussions on further enhancing the framework and its applications.
    \end{itemize}
    \vspace{1em}
    Thank you for your attention. I am now happy to answer any questions you may have.
\end{frame}
