% Section and frames
\section{Introduction to PCB Defect Detection}
\label{intro_section}

% Section title slide
\sectiontitleframe{Introduction to PCB Defect Detection}

% Frame 1: Importance and Challenges
\begin{frame}{Importance and Challenges}
    \frametitle{Importance and Challenges in PCB Defect Detection}

    \textbf{Critical Role of PCBs:}
    \begin{itemize}
        \item Essential in electronics, yet detecting defects in production is challenging.
    \end{itemize}

    \textbf{Challenges with Traditional Methods:}
    \begin{itemize}
        \item Because modern PCBs are so complex, Automatic Optical Inspection (AOI) systems frequently produce false positives.
    \end{itemize}
    
    \textbf{Need for Machine Learning:}
    \begin{itemize}
        \item focusing on the transition to machine learning (ML)-based techniques to improve defect detection accuracy.
    \end{itemize}
    \sourcespec{mahalingam2019pcb}{PCB-METAL: A PCB Image Dataset for Advanced Computer Vision Machine Learning Component Analysis}
\end{frame}

% Frame 2: Project Workflow and Approach
\begin{frame}{Project Workflow and Approach}
    \frametitle{PCB Defect Detection Workflow}

    \textbf{Stages of the Detection Workflow:}
    \begin{enumerate}
        \item Identifying defect types to be detected.
        \item Image preprocessing for ML model readiness.
        \item Development and optimization of the ML model.
    \end{enumerate}

    \textbf{Iterative Nature of the Workflow:}
    \begin{itemize}
        \item Recognizes the value of continuous improvement by adapting to new data and detection requirements.
        \item The detection tool's persevered efficacy depends on a strong testing approach.
    \end{itemize}
    
\end{frame}

% Frame 3: Importance of Image Preprocessing
\begin{frame}{Importance of Image Preprocessing}
    \frametitle{Importance of Image Preprocessing}
    %\textbf{Improves Image Data for Accurate PCB Defect Detection:}
    \textbf{The Crucial Role of Image Preprocessing in PCB Analysis:}
    \vspace{0.5em}
    \begin{itemize}
        \item To reliably identify PCB defects with machine learning models, effective image preprocessing is essential.
        \item It involves transforming raw images into a standardized format, enhancing features crucial for model analysis.
        \item Efficient preprocessing leads to improved data quality, which is essential for the model's accuracy and performance.
    \end{itemize}
    \vspace{1em}
    \sourcespec{krig2014image}{Image Pre-Processing}
\end{frame}
